Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-07-21 Paper/Poster/poster.tex
getting close to be ready

%%% Unisiegel
\begin{minipage}[c][10cm][c]{0.2\textwidth}
  \begin{center}
    \includegraphics[width=7cm,angle=0]{labrosa-logo.eps} \\
    \vspace{1cm}
    \includegraphics[width=7cm,angle=0]{seas-logo.eps}
  \end{center}
\end{minipage}
%\begin{minipage}[c][9cm][c]{0.1\textwidth}
%  \begin{center}
%    \includegraphics[width=7cm,angle=0]{seas-logo.eps}
%  \end{center}
%\end{minipage}
%%% Title
\begin{minipage}[c][9cm][c]{0.58\textwidth}
  \begin{center}
    {\sc \Huge Clustering Beat-Chroma Patterns}\\[5mm]
  {\sc \Huge in a Large Music Database}\\[10mm]
    {\Large Thierry Bertin-Mahieux $^\dagger$, Ron J. Weiss $^\ddagger$ and Daniel P. W. Ellis $^\dagger$\\[3.5mm]
     \large $\dagger$ LabROSA, Dept. of Electrical Engineering, Columbia University \\
     \large $\ddagger$ MARL, New York University \\
    \tt{\{thierry,ronw,dpwe\}@ee.columbia.edu}}
  \end{center}
\end{minipage}
%%% GK-Logo
\begin{minipage}[c][7cm][c]{0.2\textwidth}
  \begin{center}
    \includegraphics[width=10cm,angle=0]{MARL_logo_high_res.eps} \\
    \vspace{1.5cm}
    \includegraphics[width=8cm,angle=0]{nyu_music_tech_logo_2_2_bw.eps}
  \end{center}
\end{minipage}

@@

%
\begin{list}{\labelitemi}{\leftmargin=2em \labelsep=1em}
\item Goal: identify meaningful information
about the musical structure represented in the entire database by
examining individual entries in this codebook.
\item Method: identify common patterns in beat-synchronous
chromagrams by learning codebooks from a large set of examples.
Individual codewords consist of short beat-chroma patches of
between 1 and 8 beats, optionally aligned to bar boundaries.
\item Prior work: ``shingles'' of \cite{Casey2007}, 
beat-synchronous analysis to indeitfy the chorus by \cite{Bartsch2001},
and cover recognition by \cite{Ellis2007a}.
\end{list}

@@

Boring graphs on distortion, codeword size, etc, can be seen in the paper.

@@

\myfig[0]{codes_lle.ps}{.8}

@@

@@

\vspace{2cm}

\begin{minipage}[c][9cm][c]{\columnwidth}
  %\begin{center}
\textbf{Bar alignment task}.
Since the clustering described is based
on the segmentation of the signal in to bars, 
the codewords should contain information related to bar
alignment, such as the presence of a strong beat on the first beat.\\
  %\end{center}
\end{minipage}
\begin{minipage}[c][9cm][c]{0.21\textwidth}
  \begin{center}
      \begin{tabular}{cc}
        Offset & \% of times chosen \\ \hline \hline
        0 & $\mathbf{62.6}$\\
        1 & $16.5$\\
        2 & $9.4$\\
        3 & $11.5$
      \end{tabular}
      %\mytablecaption{\small{
      %    Bar alignment experiment:
      %    offsets relative to ground-truth 4-beat bar boundaries 
      %    that gave minimum distortion encodings from the bar-aligned codebook.
      %}}
      \label{tab:offset}
  \end{center}
\end{minipage}

\begin{list}{\labelitemi}{\leftmargin=2em \labelsep=1em}
\item A bullet point
\item A bullet point
\item A bullet point
\item A bullet point
\end{list}

@@

\begin{list}{\labelitemi}{\leftmargin=2em \labelsep=1em}
\item A bullet point
\item A bullet point
\end{list}

@@

% FOOTNOTE
\vspace{1cm}
\begin{minipage}{\textwidth}
\begin{small}
\begin{flushright}
Poster presented at ISMIR 2010 (Utrecht) for the paper:
Clustering Beat-Chroma Patterns in a Large Music Database by
T. Bertin-Mahieux, R. J. Weiss and D. P. W. Ellis. Contact:
\url{tb2332@columbia.edu}, code: \url{http://www.columbia.edu/~tb2332/}.
\end{flushright}
\end{small}
\end{minipage}

>>>>

%%% Unisiegel
\begin{minipage}[c][10cm][c]{0.2\textwidth}
  \begin{center}
    \includegraphics[width=7cm,angle=0]{labrosa-logo.eps} \\
    \vspace{.5cm}
    \includegraphics[width=7cm,angle=0]{seas-logo.eps}
  \end{center}
\end{minipage}
%\begin{minipage}[c][9cm][c]{0.1\textwidth}
%  \begin{center}
%    \includegraphics[width=7cm,angle=0]{seas-logo.eps}
%  \end{center}
%\end{minipage}
%%% Title
\begin{minipage}[c][9cm][c]{0.58\textwidth}
  \begin{center}
    {\sc \Huge Clustering Beat-Chroma Patterns}\\[5mm]
  {\sc \Huge in a Large Music Database}\\[10mm]
    {\Large Thierry Bertin-Mahieux $^\dagger$, Ron J. Weiss $^\ddagger$ and Daniel P. W. Ellis $^\dagger$\\[3.5mm]
     \large $\dagger$ LabROSA, Dept. of Electrical Engineering, Columbia University \\
     \large $\ddagger$ MARL, New York University \\
    \tt{\{thierry,ronw,dpwe\}@ee.columbia.edu}}
  \end{center}
\end{minipage}
%%% GK-Logo
\begin{minipage}[c][7cm][c]{0.2\textwidth}
  \begin{center}
    \includegraphics[width=10cm,angle=0]{MARL_logo_high_res.eps} \\
    \vspace{1.8cm}
    \includegraphics[width=8cm,angle=0]{nyu_music_tech_logo_2_2_bw.eps}
  \end{center}
\end{minipage}

@@

%
\begin{list}{\labelitemi}{\leftmargin=2em \labelsep=1em}
\item \textbf{Goal}: identify meaningful information
about the musical structure represented in the entire database by
examining individual entries in this codebook.
\item \textbf{Method}: identify common patterns in beat-synchronous
chromagrams by learning codebooks from a large set of examples.
Individual codewords consist of short beat-chroma patches of
between 1 and 8 beats, optionally aligned to bar boundaries.
\item Prior work: ``shingles'' of \cite{Casey2007}, 
beat-synchronous analysis to identify the chorus by \cite{Bartsch2001},
and cover recognition by \cite{Ellis2007a}.
\end{list}

@@

Additional graphs on distortion, codeword size, etc, can be seen in the paper.
As expected, a larger codebook improves distortion, longer codewords are more
difficult to learn, and a larger training set improves the results.

@@

@@

\mbox{} % dumb, but need something before vspace
\vspace{-1cm}
\myfig[0]{codes_lle.ps}{.8}

% figure caption
\begin{center}
\begin{minipage}[c]{.5\columnwidth}
\begin{small}
Possible visualization of the codebook using locally linear
embedding (LLE).
\end{small}
\end{minipage}
\end{center}

@@

\vspace{1.5cm}

\makebox[\columnwidth]{ % replace framebox by makebox for no edges

\begin{minipage}[l]{0.21\columnwidth}
  \begin{center}
      \begin{tabular}{cc}
        Offset & \% of times chosen \\ \hline \hline
        0 & $\mathbf{62.6}$\\
        1 & $16.5$\\
        2 & $9.4$\\
        3 & $11.5$
      \end{tabular}
  \end{center}
\end{minipage}

\hspace{5cm}

\begin{minipage}[r]{.5\columnwidth}
\textbf{Bar alignment task}.
Since the clustering described is based
on the segmentation of the signal in to bars, 
the codewords should contain information related to bar
alignment, such as the presence of a strong beat on the first beat.
It is the case $62\%$ of the times, see paper for details.
\end{minipage}

} % end framebox / makebox

\vspace{1.5cm}

@@

\begin{list}{\labelitemi}{\leftmargin=2em \labelsep=1em}
\item Practical method for large-scale clustering of tonal patterns.
\item Ways to inspect the resulting codebook.
\item Links to existing MIR tasks.
\item \textbf{Python code available.}
\end{list}

@@

% FOOTNOTE
\vspace{1cm}
\begin{minipage}{\textwidth}
\begin{small}
\begin{flushright}
Acknowledgements: thanks to G. Grindlay for
helpful comments. TBM is supported by a
NSERC scholarship. This material is based upon work
supported by IMLS grant LG-06-08-0073-08 and by NSF
grant IIS-0713334. \\
%Any opinions, findings and conclu-
%sions or recommendations expressed in this material are
%those of the authors and do not necessarily reflect the views
%of the sponsors.\\
Poster presented at ISMIR 2010 (Utrecht) for the paper:
Clustering Beat-Chroma Patterns in a Large Music Database by
T. Bertin-Mahieux, R. J. Weiss and D. P. W. Ellis. Contact:
\url{tb2332@columbia.edu}, code: \url{http://www.columbia.edu/~tb2332/}.
\end{flushright}
\end{small}
\end{minipage}
